Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-02-09 analysis/paper_draft3.Rmd
added line about criteria for deriving guide values for alpha

In general, by their choice of $\alpha$, the lawyer explicitly and transparently weights the historical strike data in the analysis. This transparency thwarts lawyer efforts to strategically select $\alpha$ values. Rather, at the key steps of the _Batson_ challenge process (Figure \@ref(fig:batsonworkflowfig)), the lawyers on both sides know that at any time the lawyers on the other side can always assess how sensitive any strike bias estimation is to the choice of $\alpha$. In any case, the choice of $\alpha$ cannot alone determine whether a trial judge finds that illegal bias is more likely than not (i.e., a _Batson_ violation). Future work might examine how information-criteria or data-driven approaches for selecting $\alpha$ might apply in this context. Knowing how to quantify incompatibility and specify an appropriate prior for $\alpha$ is an area of active research [e.g., @Pawel2022].

>>>>

In general, by their choice of $\alpha$, the lawyer explicitly and transparently weights the historical strike data in the analysis. This transparency thwarts lawyer efforts to strategically select $\alpha$ values. Rather, at the key steps of the _Batson_ challenge process (Figure \@ref(fig:batsonworkflowfig)), the lawyers on both sides know that at any time the lawyers on the other side can always assess how sensitive any strike bias estimation is to the choice of $\alpha$. In any case, the choice of $\alpha$ cannot alone determine whether a trial judge finds that illegal bias is more likely than not (i.e., a _Batson_ violation). Future work might examine how various criteria for deriving a guide value of $\alpha$ for types of models [e.g. @Ibrahim2015, 3724-3738] could appropriately apply in this context. Knowing how to quantify incompatibility and specify an appropriate prior for $\alpha$ is an area of active research [e.g., @Pawel2022].
